paper

### 2021-10-25 paper.Rmd
zx

```{r}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(ggtext)
library(lme4)
library(tidymodels)
library(lmerTest)
library(ggthemes)
library(ggrepel)
library(tidytext)
```

```{r}
library(rstanarm)
library(brms)
library(bayestestR)
library(BayesFactor)
```

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- read_csv("SB12.csv")
```

@@

>>>>

```{r}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(ggtext)
library(lme4)
library(tidymodels)
library(lmerTest)
library(ggthemes)
library(ggrepel)
library(tidytext)
library(rstanarm)
library(brms)
library(bayestestR)
library(BayesFactor)
```

@@

```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- read_csv("data/SB12.csv")
```

@@

```{r}
new_dt |> 
  group_by(herbicide) |> 
  summarise(control = mean(wt_28))
```
